### 2025-03-08 download-football-data.qmd
20250308 - data dictionaries

Data Dictionaries are metadata that describe the meaning of the variables in a dataset.
@Ho2025 provide Data Dictionaries for the various National Football League (NFL) datasets at the following link: <https://nflreadr.nflverse.com/articles/index.html>.

@@

This chapter extensively uses merging to process the data for later use.
See @sec-merging for a reminder of how to perform merging, the types of merges, and what you can expect when you merge data objects with different formats.
Guidance for how to merge the various NFL-related data files is provided by @Sharpe2020: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md>.

@@

A Data Dictionary for fantasy player ID data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_playerids.html>

@@

- <https://nflreadr.nflverse.com/articles/dictionary_rosters.html>
- <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#rosters>

@@

A Data Dictionary for game schedules data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_schedules.html>

@@

A Data Dictionary for game schedules data is located at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#standings>

@@

A Data Dictionary for data from the combine is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_combine.html>

@@

A Data Dictionary for draft picks data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_draft_picks.html>

@@

A Data Dictionary for draft values data is located at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#draft_values>

@@

A Data Dictionary for data from weekly depth charts is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_depth_charts.html>

@@

A Data Dictionary for game schedules data is located at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#trades>

@@

To download play-by-play data from prior weeks and seasons, we can use the `load_pbp()` function of the `nflreadr` package [@R-nflreadr].
We add a progress bar using the `with_progress()` function from the `progressr` package [@R-progressr] because it takes a while to run.
A Data Dictionary for the play-by-play data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_pbp.html>

@@

A Data Dictionary for the participation data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_participation.html>

@@

We can download historical week-by-week actual player statistics using the `load_player_stats()` function from the `nflreadr` package [@R-nflreadr].
A Data Dictionary for statistics for offensive players is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
A Data Dictionary for statistics for defensive players is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.

@@

A Data Dictionary for injury data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_injuries.html>

@@

A Data Dictionary for snap counts data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_snap_counts.html>

@@

A Data Dictionary for ESPN QBR data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_espn_qbr.html>

@@

A Data Dictionary for NFL Next Gen Stats data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_nextgen_stats.html>

@@

A Data Dictionary for Pro Football Reference passing data is located at the following links:

- <https://nflreadr.nflverse.com/articles/dictionary_pfr_passing.html>
- <https://www.pro-football-reference.com/about/advanced_stats.htm>

Advanced stats from the 2024 season are available at the following link: <https://www.pro-football-reference.com/years/2024/advanced.htm>

@@

A Data Dictionary for player contracts data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_contracts.html>

@@

A Data Dictionary for FTN Charting data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ftn_charting.html>

@@

A Data Dictionary for FantasyPros ranking data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_rankings.html>

@@

A Data Dictionary for expected fantasy points data is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_opportunity.html>

@@

Now, modify the scoring settings to match your league settings.
Below, we use the [scoring settings](https://support.nfl.com/hc/en-us/articles/4989179237404-Scoring) for fantasy leagues on NFL.com, which happen to be point-per-reception leagues (i.e., PPR leagues):

>>>>

Data Dictionaries are metadata that describe the meaning of the variables in a dataset.
@HoDataDictionaries provide Data Dictionaries for the various National Football League (NFL) datasets at the following link: <https://nflreadr.nflverse.com/articles/index.html>.

@@

This chapter extensively uses merging to process the data for later use.
See @sec-merging for a reminder of how to perform merging, the types of merges, and what you can expect when you merge data objects with different formats.
Guidance for how to merge the various NFL-related data files is provided by @SharpeNFLDataSets: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md>.

@@

@HoFFPlayerIDs provide a Data Dictionary for fantasy player ID data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_playerids.html>

@@

- <https://nflreadr.nflverse.com/articles/dictionary_rosters.html> [@HoRosters]
- <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#rosters> [@SharpeRosters]

@@

@HoSchedules provide a Data Dictionary for game schedules data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_schedules.html>

@@

@SharpeStandings provides a Data Dictionary for standings data at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#standings>

@@

@HoCombine provide a Data Dictionary for data from the combine at the following link: <https://nflreadr.nflverse.com/articles/dictionary_combine.html>

@@

@HoDraftPicks provide a Data Dictionary for draft picks data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_draft_picks.html>

@@

@SharpeDraftValues provides a Data Dictionary for draft values data at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#draft_values>

@@

@HoDepthCharts provide a Data Dictionary for data from weekly depth charts at the following link: <https://nflreadr.nflverse.com/articles/dictionary_depth_charts.html>

@@

@SharpeTrades provides a Data Dictionary for NFL trade data at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#trades>

@@

To download play-by-play data from prior weeks and seasons, we can use the `load_pbp()` function of the `nflreadr` package [@R-nflreadr].
We add a progress bar using the `with_progress()` function from the `progressr` package [@R-progressr] because it takes a while to run.
@HoPBP provide a Data Dictionary for the play-by-play data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_pbp.html>

@@

@HoParticipation provide a Data Dictionary for the participation data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_participation.html>

@@

We can download historical week-by-week actual player statistics using the `load_player_stats()` function from the `nflreadr` package [@R-nflreadr].
@HoPlayerStats provide a Data Dictionary for statistics for offensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
@HoPlayerStatsDefense provide a Data Dictionary for statistics for defensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.

@@

@HoInjuries provide a Data Dictionary for injury data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_injuries.html>

@@

@HoSnapCounts provide a Data Dictionary for snap counts data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_snap_counts.html>

@@

@HoQBR provide a Data Dictionary for ESPN QBR data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_espn_qbr.html>

@@

@HoNextGenStats provide a Data Dictionary for NFL Next Gen Stats data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_nextgen_stats.html>

@@

There is a Data Dictionary for Pro Football Reference passing data at the following links:

- <https://nflreadr.nflverse.com/articles/dictionary_pfr_passing.html> [@HoPFRPassing]
- <https://www.pro-football-reference.com/about/advanced_stats.htm> [archived at <https://perma.cc/LKH5-92PQ>; @PFR2025]

@PFR2024 provides advanced stats from the 2024 season at the following link: <https://www.pro-football-reference.com/years/2024/advanced.htm>

@@

@HoContracts provide a Data Dictionary for player contracts data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_contracts.html>

@@

@HoFTNCharting provide a Data Dictionary for FTN Charting data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ftn_charting.html>

@@

@HoFantasyProsRankings provide a Data Dictionary for FantasyPros ranking data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_rankings.html>

@@

@HoOpportunity provide a Data Dictionary for expected fantasy points data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_opportunity.html>

@@

Now, modify the scoring settings to match your league settings.
Below, we use the [scoring settings](https://support.nfl.com/hc/en-us/articles/4989179237404-Scoring) for fantasy leagues on [NFL.com](https://www.nfl.com), which happen to be point-per-reception leagues (i.e., PPR leagues):
